Highly Available Transactions: Virtues and Limitations

### 2013-03-28 writeup/evaluation.tex
moar writin

In summary, many---but not all---TPC-C transactions are well-served by
HATs. The two problematic transactions---New-Order and Payment---rely
on non-monotonic state updates. The former transaction can be modified
to ensure ID uniqueness at the expense of sequential per-district ID
ordering, while the latter is an inherently non-monotonic action
requiring external compensation or stronger consistency protocols. We
expect that, especially for read-dominated workloads found in many
online services, HAT guarantees may suffice for many
applications. Finally, while TPC-C is not subject to write skew
anomalies, we note that many TPC-E isolation tests, such as one that
requires simultaneously modifying a product description and its image,
are satisfied by HATs.

>>>>

In summary, many---but not all---TPC-C transactions are well-served by
HATs. The two problematic transactions---New-Order and Payment---rely
on non-monotonic state update. The former transaction can be modified
to ensure ID uniqueness at the expense of sequential per-district ID
ordering, while the latter is an inherently non-monotonic action
requiring external compensation or stronger consistency protocols. We
expect that, especially for read-dominated workloads found in many
online services, HAT guarantees will suffice for many
applications. Finally, while TPC-C is not subject to write skew
anomalies, we note that many TPC-E isolation tests, such as one that
requires simultaneously modifying a product description and its image,
are satisfied by HATs.

### 2013-03-28 writeup/futurework.tex
moar writin

\section{Future Work}

VII. Future Work (.75pg)

* What properties are available?
	* We've focused on ACID Isolation, but there are lots of other models to consider?
	* Which consistency criteria? Which models? There are infinite, so how do we choose?
	* Set ourselves up for APEs

* Full exploration of HAT space
	* Many parameters; $2^10$ models at the least
	* Need to mitigate the cost of tracking causality with high availability
		* The cost moving from S-HA (like Eiger) to truly HA (R-HA) seems to be high
		* e.g., Eiger relies on metadata GC to keep writes small; is O(|keys|) in limit
			* Not meant as a fault--it's optimized for a particular scenario--but curious to consider

* Revisit semantics-based concurrency control
	* Could taxonomize properties like escrow
	* Can also consider models with SLAs and bounded messaging asynchrony
	* Our focus is on "classic" distributed systems trade-off
		* However, lots of interesting hybrids (maybe cite Doug Terry's recent stuff)

>>>>

\section{Future Work}
\label{sec:futurework}

We believe that there are several promising avenues for future work in
Highly Available Transaction systems:

\textbf{What is the space of consistency and isolation properties?} In
this work, we have taxonomized several well-defined and
well-documented consistency properties. This is useful as it
contextualizes decades of existing database and distributed systems
design and algorithms but does not provide guidance as to what
consistency models are the ``strongest''---or admit the smallest set
of executions---within each availability class. A recent report from
UT Austin shows that no model stronger than causal consistency can be
achieved in a sticky highly available, one-way convergent
system~\cite{cac}, but there are infinite highly available and sticky
highly available models to consider. For example, always returning the
value $1$ in response to reads is incomparable with (i.e., neither
stronger nor weaker than) causal consistency: returning $1$ does not
respect causality, and causal consistency returns values other than
$1$. Always returning the value $2$ is similarly incomparable, and, as
an example, we can enumerate models that return all integers and real
numbers--an uncountably infinite set of models. Given these infinite
models, are there meaningful properties that delineate the boundaries
between classes of highly available systems? Is there a
``meta-property'' that exactly characterizes what properties are
achievable with high availability or sticky high availability? This is
an area of ongoing research within the Berkeley HAT project.

\textbf{What are the costs and benefits within HAT designs?} There are
many possible combinations of HAT guarantees, and the performance and
ease of implementation of a HAT system will vary depending on which
guarantees it provides. For example, as we have discussed, the cost in
moving from a sticky high available implementation of highly available
guarantees to a truly highly available system seems expensive for some
models (e.g., metadata requirements or visibility requirements may
become problematic). Further experimentation regarding the set of
useful and achievable HAT guarantees will shed further light on this
question.

\textbf{Where do semantics-based concurrency control and weakened
  failure models lie in the HAT landscape?} The vast amount of
literature on semantics-based concurrency control provides hints as to
when coordination can be avoided while providing ``strongly
consistent'' outcomes for limited failure scenarios. We have performed
a narrow case study in this work, but a general taxonomization of
techniques such as escrow transactions~\cite{escrow} and
Sagas~\cite{sagas} could help answer the challenge of programming in a
weakly consistent environment. Additionally, HAT guarantees can be
strengthened by considering failure models with, say, bounded
asynchrony or service-level agreements from underlying
hardware. Additionally, while we have focused on systems that provide
a single availability mode, there are several interesting hybrids to
consider.
